LAGOS lake depth

### 2020-06-09 manuscript/manuscript.Rmd
add inline tables

@@

>>>>

\begin{table}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
  \hline
  Variable & Median & Q25 & Q75 & n\\
  \hline
  Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4850 (17700)\\
  \textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4850 (17700)\\
  \textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4850 (17700)\\
  \textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4850 (17700)\\
  \textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4850 (17700)\\
  \textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4850 (17700)\\
  \textbf{Watershed-lake ratio} & 7.8 (10) & 3.9 (4.4) & 17 (28) & 4850 (17700)\\
  Distance to deepest point (m) & 180 (-) & 110 (-) & 290 (-) & 4850 (-)\\
  Distance to lake center (m) & 240 (-) & 160 (-) & 380 (-) & 4850 (-)\\
  In-lake slope (m/m) & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4850 (-)\\
  Nearshore land slope (m/m) & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4850 (-)\\  
  \bottomrule
  \end{tabular}
  \caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States from <LAGOSUS-Depth citation>). Predictor variables for computing random forest offsets (Eq 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{table1}
\end{table}

@@

\begin{table}
  \centering
  % \setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{llll}
  \hline
  slope & distance & rmse & rsq\\
  \hline
  true & true & - & -\\
  true & proxy & 4.2 m & 0.73\\
  proxy & true & 6.9 m & 0.26\\
  proxy & proxy & 6.6 m & 0.31\\
  \bottomrule
\end{tabular}
\caption{Model fit and predictive accuracy metrics (RMSE = root mean square error, $R^2$ = coefficient of determination) for all combinations of true (in-lake slope, distance to the deepest point of the lake) and proxy (nearshore land slope, distance to lake center) metrics.} \label{table2}
\end{table}

### 2020-06-09 tables/01_predictors.Rmd
add inline tables

---
output:
  pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

@@

# bold Eq 2 predictor variables
dt$Variable[!stringr::str_detect(dt$Variable, "slope|Distance|depth")] <- 
  paste0("**", 
         dt$Variable[!stringr::str_detect(dt$Variable, "slope|Distance|depth")],
         "**")

options(knitr.kable.NA = '-')
knitr::kable(dt, digits = 0, format = "markdown") 
```

>>>>

---
output:
  pdf_document
header-includes: 
  - \pagenumbering{gobble}
editor_options: 
  chunk_output_type: console
---

@@

# bold Eq 2 predictor variables
dt_md <- dt
dt_md$Variable[!stringr::str_detect(dt_md$Variable, "slope|Distance|depth")] <- 
  paste0("**", 
         dt_md$Variable[!stringr::str_detect(dt_md$Variable, "slope|Distance|depth")],
         "**")

options(knitr.kable.NA = '-')
knitr::kable(dt_md, digits = 0, format = "markdown")

# ---- latex output ----

# bold Eq 2 predictor variables
dt$Variable[!stringr::str_detect(dt$Variable, "slope|Distance|depth")] <- 
  paste0("\\textbf{", 
         dt$Variable[!stringr::str_detect(dt$Variable, "slope|Distance|depth")],
         "}")

# clipr::write_clip(
#   knitr::kable(dt, format = 'latex', align = c("lllll"), escape = FALSE))
```
